Lensing

### 2015-05-15 Papers/ms.tex
A little bit of writing

\section{Introduction}
Galaxy-galaxy lensing is a powerful astrophysical tool for studying
the distribution of matter, including dark matter, in galaxies
\citep{treu}. In recent years, several lens systems have been discovered which
are thought to contain at least one dark substructure
\citep{vegetti1, vegetti2, vegetti3}. In this paper we address the topic of
inferring the matter distribution in the lens galaxy from the lensed,
blurred image. These approaches may be categorized according to
Whether to use a simply parameterized (e.g. Sérsic)
or flexible (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain

@@

>>>>

\section{Introduction}
Galaxy-galaxy lensing is a powerful astrophysical tool for studying
the distribution of matter, including dark matter, in galaxies
\citep{treu}. It holds substantial potential as a technique for discovering
and measuring the properties of dark matter substructures \citep{koopmans}.
In recent years, this potential has been realised in several lens systems
which are thought to contain at least one dark substructure
\citep{vegetti1, vegetti2, vegetti3}.

In this paper we address the topic of
inferring the matter distribution in the lens galaxy from the lensed,
blurred image. These approaches may be categorized according to the following
criteria:
\begin{enumerate}
\item Whether to use a simply parameterized (e.g. Sérsic), moderately flexible
(e.g. mixture model, \citet{2011MNRAS.412.2521B})
or free-form (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain

@@

\bibitem[\protect\citeauthoryear{Koopmans}{2005}]{koopmans} 
Koopmans L.~V.~E., 2005, MNRAS, 363, 1136
